Lensing

### 2014-12-13 Papers/ms.tex
MNRAS format

% Every Latex document starts with a documentclass command
\documentclass[a4paper, 11pt]{article}

% Load some packages
\usepackage{graphicx} % This allows you to put figures in
\usepackage{epstopdf}
\usepackage{natbib}   % This allows for relatively pain-free reference lists
\usepackage[left=3cm,top=3cm,right=3cm]{geometry} % The way I like the margins

@@

% This helps with figure placement
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

% Set values so you can have a title
\title{}
\title{Flexible trans-dimensional modelling of gravitational lenses}
\author{Brendon J. Brewer$^1$, David Huijser$^1$, and
Geraint F. Lewis$^2$}
\date{\small $^1$ Department of Statistics, The University of Auckland\\
Private Bag 92019, Auckland 1142, New Zealand\\
$^2$ Sydney Institute for Astrophysics\\
\vspace{1cm}
{\tt bj.brewer@auckland.ac.nz}}
% Document starts here
\begin{document}

% Actually put the title in
\maketitle

\abstract{Gravitational lensing is a powerful astrophysical tool for studying
the distribution of matter in galaxies.}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}

\voffset=-0.8in

% Packages:
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{dsfont}

@@

\title[]
{Lensing}

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\date{To be submitted to MNRAS}

\maketitle

\label{firstpage}

\begin{abstract}
Gravitational lensing is a powerful astrophysical tool for studying
the distribution of matter in galaxies.
\end{abstract}

\begin{keywords}
methods: data analysis --- methods: statistical
\end{keywords}
